\chapter{Introduction}\label{chpt:introduction}
Surveillance is becoming an increasingly more important aspect in present day. In an attempt to increase the safety of its citizens, governments all over the world install public cameras\cite{city_surveillance}. At the same time the dream of intelligent robots with human-like behaviour, as depicted in movies such as "I, Robot"\cite{imdb_robot}, is nearing. Development of artificial intelligence is a hot topic in 2015, and several experts predict that  soon will be an integral element of everyday life\cite{ai_microsoft}.

An important element of programming machines to exercise human-like behaviour is the ability to sense and interact with their environment. Giving a machine senses is one thing, but teaching the machine how to react on these sensing inputs is an extremely complex task\cite{facebook_ai}. A problem as simple as using a camera to simulate vision and then finding and recognising a complex object, such as the face of a person, is a computationally heavy task\cite{ai_facial_recog}.

%Recognition can also be used in a militaristic context. A system could be able to recognise objects, say an enemy vehicle, and follow this vehicle's movement, waiting for permission to fire\cite{rockwell_system}. Soldiers in the field could then carry a device that they could quickly be set up and use for monitoring an area, perhaps even with several cameras to have a greater  to monitor. Another system could be set up to monitor and protect embassies in foreign countries by tracking and shooting unrecognised intruders.

%værdifulde genstande
Recognition is also used for security systems in buildings with valuable possessions. Such a location could be a museum with irreplaceable objects like paintings and other artefacts, which need to be kept safe from intruders. The challenges this system could face are tasks such as monitoring a 3D space, identifying and distinguishing valuable artefacts from objects of no interest and continue tracking them in motion.

This project aims to build a simplified version of the museum security system and explores the theme of surveillance, in connection with embedded devices, with the primary focus of creating a targeting platform that is able to recognise a predefined object. The system will incorporate a secondary focus of tracking the object with the intention of notifying some second system to ensure the safety of the predefined object.
