\chapter{Sprint 4}
This is the last sprint and will be dedicated to implementing final features discovered in \cref{cha:sprint3} and improving the overall code quality. This includes implementing some of the functionality discussed in \cref{sec:secure}, and preparing the code for handing over to the new developers. Additionally, a section will be prepared for future developers to ease the transition and make it easier to get started.


\input{4sprint/intermediate_server_update}
\input{4sprint/client_server_update}
\input{4sprint/catch_up}

\section{Code Inspection}
Since this project will be further developed by other people, we find it essential to perform a final review of the code to improve readability.

By using the IntelliJ IDEA we are able to use one of the built-in tools, called \emph{Inspect code}, to analyse the code and suggest improvements. This is done for RESTsw6, indoorCore and indoorLibrary. When inspecting code, we receive suggestions in different categories: Class structure, declaration redundancy, Imports, etc. Class structure concerns suggestions related to moving global variable into a sub scope where they are used to hide information. Declaration redundancy concerns variable access level and removing redundant code such as empty methods and unused parameters. Imports relates to unused packages. We also receive notifications in regards to possible bugs as a result of constants concealed as variables.

It is important to remember that the tool only gives suggestions. Inspect code is a static review of the code, and does not perform an analysis of the code under execution. Consequently it is not able to see how a class or method is used, which sometimes results in unrealistic suggestions that are more likely to break the code.

\section{Sprint Evaluation}
To perform an evaluation of the sprint we iterate over the sprint goals and comment on whether or not they were fulfilled.

We set out to update both the intermediate server and the client server following the security considerations made in \cref{sec:secure}. These updates successfully implemented several features as well as refactored the code to streamline style and improve the overall code quality with the help of a inspection tool.

Finally, we planned on preparing a section dedicated to ease the transitioning for future developers. \Cref{sec:catchup} contains information on how to perform different tasks and solve problems that are essential for the project.